---
title: "ageR: Supervised Age Modelling"
author: 
  - "Roberto Villegas-Diaz"
date: '2020-11-06'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    # includes:
    #   after_body: insert-logo.html
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
xaringanthemer::style_mono_accent(
  base_color = "#2f4174",
  inverse_header_color = "#FFFFFF"
)
```
## What data do you need?
- __Core:__ `labID`, `age`, `error`, `depth`, and `cc`
- __Sampling:__ `ID` and `depth`
- __(Optional) Hiatuses:__ `ID` and `depth`

## How do you get the data?
- A comma-separated values (CSV) file
- A query to a database

---
## Installation
Current version can be installed from the GitHub repository:
```{r install-dev, eval = FALSE}
install.packages("remotes")
remotes::install_github("special-uor/ageR")
```

To verify you are running the latest version, run the following command:
```{r check-install, eval = FALSE}
?ageR
```

---
class: inverse, center, middle
# Demo

---
## Example (Toy data)
### File structure
```{r bacon-file-structure}
ageR::file_structure(entity = "X", am = "bacon")
```

---
### Input data
#### Core data
```{r bacon-create-input-step2}
core <- data.frame(labID = paste0("X", sprintf("%03d", 1:5)),
                   age = c(50, 200, 1150, 2060, 4050),
                   error = c(10, 15, 5, 1, 70),
                   depth = c(5, 100, 230, 300, 450),
                   cc = 1)
knitr::kable(core)
```

---
### Input data (2)
#### Sampling depths
```{r bacon-create-input-step1}
sample_depths <- data.frame(id = 1:100,
                            depth = seq(0, 500, length.out = 100))
knitr::kable(head(sample_depths))
```

---
### Input data (3)
#### (Optional) Hiatuses
```{r bacon-create-input-step3}
hiatus <- data.frame(id = c(1, 2),
                     depth = c(50, 150))
knitr::kable(hiatus)
```
---
### Input data (4)
```{r bacon-create-input-step4, eval = TRUE}
ageR::create_input(data = list(sample_depths = sample_depths, 
                               core = core,
                               # Optional
                               hiatus = NULL,
                               not_used = NULL), 
                   wdir = "./", 
                   entity = "X",
                   am = "bacon")
```
---
### Databases: RPD
```{r}
conn <- dabr::open_conn_mysql("RPD-latest")
query <- paste0(
"SELECT entity_name,
       entity.ID_ENTITY as entity_id,
	     lab_number AS labID,
       age_C14 AS age,
       error,
       avg_depth*100 AS depth,
       date_type,
       thickness
FROM date_info INNER JOIN entity
    ON date_info.ID_ENTITY = entity.ID_ENTITY
WHERE latitude >= 45")

rpd <- dabr::select(conn, query, quiet = TRUE)
nrow(rpd)
```

---
### Databases: RPD (2)
```{r}
`%>%` <- dplyr::`%>%`
rpd <- rpd %>%
  dplyr::filter(!is.na(age)) %>%
  dplyr::filter(!is.na(error)) %>%
  dplyr::filter(!is.na(depth)) %>%
  dplyr::mutate(error =  ifelse(error <= 0, 1, error)) %>%
  dplyr::arrange(depth) %>%
  dplyr::mutate(cc = ifelse(grepl("*carbon", date_type), 1, 0))

entities <- sort(unique(rpd$entity_name))
head(entities)
```

---
### Databases: RPD (3)
```{r}
test_entity <- "Burnt Knob core 1"
test_entity_id <- unique(rpd$entity_id[rpd$entity_name == test_entity])

# Extract sampling depths
query <- paste0("SELECT ID_SAMPLE AS id, sample_depth*100 AS depth
                 FROM sample
                 WHERE ID_ENTITY = ", test_entity_id)
sample_tb <- dabr::select(conn, query, quiet = TRUE)
sample_tb <- sample_tb %>%
  dplyr::filter(depth != -9999)

# Extract core data
my_core <- rpd[rpd$entity_name == test_entity, 
               c("labID", "age", "error", "depth", "cc")]

# Create input
ageR::create_input(data = list(core = my_core, 
                               sample_depths = sample_tb), 
                   wdir = "./", 
                   entity = test_entity)
```
---
### Run Bacon
```{r bacon-run-fx-call, eval = FALSE}
ageR::Bacon(wdir = "./", 
            entity = "X", 
            # Optional parameters
            cpus = 1,
            postbomb = 0,
            cc = 0,
            seed = NA,
            alt_depths = NULL,
            quiet = FALSE,
            acc_step = 5,
            acc_lower = NULL,
            acc_upper = NULL,
            thick_step = 5,
            thick_lower = NULL,
            thick_upper = NULL,
            dry_run = FALSE,
            ...)
```

More details: https://special-uor.github.io/ageR/reference/Bacon
---
### Run Bacon: Dry-run
```{r bacon-run-dr}
out <- ageR::Bacon(wdir = "./", entity = "X", dry_run = TRUE, quiet = TRUE)
```
---
### Run Bacon: Mixed calibration curves
```{r bacon-mixed-cc}
ccdir <- "./ccurves"
ageR::mix_curves(proportion = 0.5, 
                 cc1 = 1, 
                 cc = 3, 
                 name = "neotropics.14C", 
                 dirname = ccdir)
```

```{r, eval = FALSE}
out <- ageR::Bacon(wdir = "./", 
                   entity = "X", 
                   cc4 = "neotropics.14C", 
                   ccdir = ccdir)
```
---
## Wishlist (aka GitHub issues)

Create new "Issues" to request new features, report an error, etc.

https://github.com/special-uor/ageR/issues

---
class: center, middle

# Thanks!

Slides created using the R package [**xaringan**](https://github.com/yihui/xaringan).

```{r cleanups, include = FALSE}
unlink("X", recursive = TRUE, force = TRUE)
unlink("ccurves", recursive = TRUE, force = TRUE)
unlink("Burnt Knob core 1", recursive = TRUE, force = TRUE)
```
