---
title: "ageR: Supervised Age Modelling"
author: 
  - "Roberto Villegas-Diaz"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
xaringanthemer::style_mono_accent(
  base_color = "#2f4174",
  inverse_header_color = "#FFFFFF"
)
```
## What data do you need?
- __Core:__ `labID`, `age`, `error`, `depth`, and `cc`
- __Sampling:__ `ID` and `depth`
- __(Optional) Hiatuses:__ `ID` and `depth`

## How do you get the data?
- A comma-separated values (CSV) file
- A query to a database

---
## Example (Toy data)
### File structure
```{r bacon-file-structure}
ageR::file_structure(entity = "X", am = "bacon")
```

---
### Input data
#### Core data
```{r bacon-create-input-step2}
core <- data.frame(labID = paste0("X", sprintf("%03d", 1:5)),
                   age = c(50, 200, 1150, 2060, 4050),
                   error = c(10, 15, 5, 1, 70),
                   depth = c(5, 100, 230, 300, 450),
                   cc = 1)
knitr::kable(core)
```

---
### Input data (2)
#### Sampling depths
```{r bacon-create-input-step1}
sample_depths <- data.frame(id = 1:100,
                            depth = seq(0, 500, length.out = 100))
knitr::kable(head(sample_depths))
```

---
### Input data (3)
#### (Optional) Hiatuses
```{r bacon-create-input-step3}
hiatus <- data.frame(id = c(1, 2),
                     depth = c(50, 150))
knitr::kable(hiatus)
```
---
### Input data (4)
```{r bacon-create-input-step4, eval = TRUE}
ageR::create_input(data = list(sample_depths = sample_depths, 
                               core = core,
                               # Optional
                               hiatus = hiatus), 
                   wdir = "./", 
                   entity = "X",
                   am = "bacon")
```

---
### Run Bacon
```{r bacon-run-fx-call, eval = FALSE}
ageR::Bacon(wdir = "./", 
            entity = "X", 
            # Optional parameters
            cpus = 1,
            postbomb = 0,
            cc = 0,
            seed = NA,
            alt_depths = NULL,
            quiet = FALSE,
            acc_step = 5,
            acc_lower = NULL,
            acc_upper = NULL,
            thick_step = 5,
            thick_lower = NULL,
            thick_upper = NULL,
            dry_run = FALSE,
            ...)
```
---
### Run Bacon (2)
#### Dry-run
```{r bacon-run-dr}
ageR::Bacon(wdir = "./", entity = "X", dry_run = TRUE, quiet = TRUE)
```
<!-- ## Example -->
<!-- ```{r, eval = TRUE} -->
<!-- `%>%` <- dplyr::`%>%` -->
<!-- conn <- dabr::open_conn_mysql("RPD-latest") -->
<!-- query <- paste0("SELECT entity_name,  -->
<!--                         entity.ID_ENTITY AS entity_id,  -->
<!--                         lab_number AS labID,  -->
<!--                         age_C14 AS age,  -->
<!--                         error,  -->
<!--                         avg_depth*100 AS depth,  -->
<!--                         date_type,  -->
<!--                         thickness -->
<!--                   FROM date_info INNER JOIN entity -->
<!--                   ON date_info.ID_ENTITY = entity.ID_ENTITY -->
<!--                   WHERE latitude >= 45") -->
<!-- rpd <- dabr::select(conn, query, quiet = TRUE) -->
<!-- rpd <- rpd %>% -->
<!--   dplyr::filter(!is.na(age)) %>% -->
<!--   dplyr::filter(!is.na(error)) %>% -->
<!--   dplyr::filter(!is.na(depth)) %>% -->
<!--   dplyr::mutate(error =  ifelse(error <= 0, 1, error)) %>% -->
<!--   dplyr::arrange(depth) %>% -->
<!--   dplyr::mutate(cc = ifelse(grepl("*carbon", date_type), 1, 0)) -->
<!-- ``` -->

---
## Wishlist (aka Github issues)

Create new "Issues" to request new features, report an error, etc.

https://github.com/special-uor/ageR/issues

---
class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
